### 2021-12-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@c2429146b928e0e2a7813e8721eac630a5aced5b 🚀

In this section, we will change the values of \(b\) abd \(s\) for a
given value of \(\rho\), and see how the values of common performance
measures for binary classification are affected. Specifically, we will
focus on four quantities: the accuracy
(\((\text{tp}+\text{tn})/(\text{tp}+\text{tn}+\text{fp}+\text{fn})\)),
the \emph{balanced} accuracy
(\(\text{tp}/(2(\text{tp}+\text{fn}))+\text{tn}/(2(\text{tn}+\text{fp}))\)),
Youden's J
(\(\text{tp}/(\text{tp}+\text{fn})+\text{tn}/(\text{tn}+\text{fp})-1\)),
and the \(F_1\) score (\(2\text{tp}/(2\text{tp}+\text{fp}+\text{fn})\)).

\textbf{Justification} of why these 4

Assuming a no-skill unbiased classifier (\(s=0.5\), \emph{i.e.}
\(\mathbf{C}=\mathbf{M}\) after normalization), the accuracy is
\(\rho^2 + (1-\rho)^2\), the balanced accuracy is \(0.5\), Youden's J is
\(0\), and \(F_1=\rho\). In other words, given a connectance
\(\rho = 0.05\), we expect that a classifier guessing at random would
still achieve an accuracy of \(0.905\); for a connectance of
\(\rho = 0.01\), this accuracy \emph{increases} to over \(0.98\). In
other words, networks with fewer interactions have inherently higher
accuracy, because it is easy to predict the overwheling majority of
non-interactions right.

In order to examine how these values change w.r.t. the skill and bias,
we performed a grid exploration of the values of \(\text{logit}(s)\) and
\(\text{logit}(b)\) linearly from \(-10\) to \(10\), and visualize the
result for a connectance of \(\rho = 0.15\), which is within the range
of usually observed connectance values for empirical food webs.

>>>>

In this section, we will change the values of \(b\), \(s\), and
\(\rho\), and report how the main measures discussed in the introduction
(MCC, \(F_1\), \(\kappa\), and informedness) are responding to issues
with the classifier. Before we do so, it is important to explain why we
will not focus on accuracy too much. Accuracy is the number of correct
predictions (\(\text{Tr}(\mathbf{C})\)) divided by the sum of the
confusion matrix. For a no-skill, no-bias classifier, accuracy is equal
to \(\rho^2 + (1-\rho)^2\); for \(\rho = 0.05\), this is
\(\approx 0.90\), and for \(\rho = 0.01\), this is equal to
\(\approx 0.98\). In other words, the values of accuracy are expected to
be so high that they are not really informatived (this is simply
explained by the fact that for \(\rho\) small,
\(\rho^2 \ll (1-\rho)^2\)). More concerning is the fact that introducing
bias changes the response of accuracy in unexpected ways. Assuming a
no-skill classifier, the numerator of accuracy becomes
\(b\rho^2 + (1-b)(1-\rho)^2\), which increases when \(b\) is low, which
specifically means that at equal skill, a classifier that under-predicts
interactions will have higher accuracy than an un-biased classifier.
These issues are absent from balanced accuracy, but should nevertheless
lead us to not report accuracy as the primary measure of network
prediction success; moving forward, we will focus on other measures.

In order to examine how MCC, \(F_1\), \(\kappa\), and informedness
change w.r.t. the imbalance, skill, and bias, we performed a grid
exploration of the values of \(\text{logit}(s)\) and \(\text{logit}(b)\)
linearly from \(-10\) to \(10\), of \(\rho\) linearly in \(]0, 0.5]\),
which is within the range of usually observed connectance values for
empirical food webs. Note that at this point, there is no food web model
to speak of; rather, the confusion matrix we discuss can be obtained for
any classification task.
